Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-06-03 main.tex
PB: edit abstract

\begin{abstract}%% (Must be 250 Words)
Spectral energy distribution (SED) of a galaxy contains information about the physical properties of it.
Classifying SEDs using temples helps understand the nature of the source of SEDs.
However, available SED templates are limited, which makes finding type of SEDs tricky.
Most of the current classifying methods cannot classify SEDs outside the ones in the template, and will fail in the special cases.
In this paper, we introduced a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
SOM is a type of the artificial neural networks, which mostly is used to identify subgroups in a sample.
We utilized an unsupervised self-organizing map (SOM) as a method to train networks using templates of SEDs ranging from far ultraviolet (FUV) to near infrared (NIR) wavelengths.
Then, we used the trained networks to cluster a sample of 142 galaxies with 0.5 < $z$ < 1.
Since, some the SEDs of these galaxies are not exactly the same as the ones in the template, the previous attempts to classifying SEDs of this group of galaxies were not completely successful. 
By using SOM, we classify those special SEDs and show that they have similarities to two more of the template ones.
We investigated the vapidity of our results, by studying the SEDs, and some physical properties of the galaxies that are averaged over galaxies in each neuron the SOMs.

>>>>

\begin{abstract}%% (Must be 250 Words)
The spectral energy distribution (SED) of a galaxy contains information about its physical properties.
Classifying SEDs using templates helps elucidate the nature of a galaxy's energy sources.
However, available templates are limited, which can complicate SED classification.
Most current classification methods cannot classify SEDs outside the range of templates, and will fail in special cases.
In this paper, we introduce a new method of classifying the spectral
energy distributions of high redshift galaxies: the self-organizing map.
Self-organizing maps are a type of artificial neural network, mostly used to identify subgroups in a sample.
We trained an unsupervised self-organizing map networks using a set of
galaxy SED templates covering the wavelength range from far ultraviolet to near infrared.
The trained networks were used to cluster the SEDs of a sample of 142 galaxies with $0.5 < z < 1$.
Compared to previous attempts to classify this sample, the
self-organizing map approach was able to better classify the SEDs with
similarities to more than one template.
The averaged SEDs and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
